%
%\nocite{*}
%\begingroup
%\setstretch{1.2}
%%\setlength\bibitemsep{0pt}
%\printbibliography[title=Publications]
%\endgroup
%
\section{Publications}%
\raisebox{\baselineskip}[0pt][0pt]{\phantomsection}\label{Publications}
%

\textbf{In preparation}:%in submission准备中
\setstretch{1.2}%
\begin{etaremune}[label={[\reversearabic*]},leftmargin=0.041\textwidth,itemsep=0pt]
	%\begin{etaremune}[leftmargin=0.025\textwidth,itemsep=0pt]
	\item \fullcite{xcz1}
	\item \fullcite{xcz2}
\end{etaremune}
\textbf{Journal article}:
\begin{etaremune}[label={[\reversearabic*]},leftmargin=0.041\textwidth,itemsep=0pt]
	%\begin{etaremune}[leftmargin=0.025\textwidth,itemsep=0pt]
	\item \fullcite{chenLaserNanoprinting3D2023a}
	\item \fullcite{guoSpatiallyStructuredModeMultiplexing2023a}
\end{etaremune}
\textbf{Software copyright}:
\begin{etaremune}[label={[\reversearabic*]},leftmargin=0.041\textwidth,itemsep=0pt]
	%\begin{etaremune}[leftmargin=0.025\textwidth,itemsep=0pt]
%	\item Photoshop. [Version 22.4.2]. Adobe Systems Incorporated. 登字第R-000001. 2021. 美国加州.
	\item \textbf{C. Xie}, \href{https://github.com/ChenZhu-Xie/Stardust_DDTank}{\textit{Stardust DDTank charge-mode auxiliary tool.apk}}, [Ver 1.0], \href{https://register.ccopyright.com.cn/query.html}{ID. }2019SR0530474, \href{https://register.ccopyright.com.cn/query.html}{Beijing, China.}
	\item \textbf{C. Xie}, \href{https://github.com/ChenZhu-Xie/Stardust_DDTank}{\textit{Stardust DDTank drag-mode auxiliary tool.exe}}, [Ver 1.0], \href{https://register.ccopyright.com.cn/query.html}{ID. }2019SR0390880, \href{https://register.ccopyright.com.cn/query.html}{Beijing, China.}
	\item \textbf{C. Xie}, \href{https://github.com/ChenZhu-Xie/Stardust_DDTank}{\textit{Stardust DDTank-Browser auxiliary tool.exe}}, [Ver 1.0], \href{https://register.ccopyright.com.cn/query.html}{ID. }2019SR0435497, \href{https://register.ccopyright.com.cn/query.html}{Beijing, China.}
	\item \textbf{C. Xie}, \href{https://github.com/ChenZhu-Xie/Stardust_DDTank}{\textit{Stardust DDTank-mobile auxiliary tool.exe}}, [Ver 1.0], \href{https://register.ccopyright.com.cn/query.html}{ID. }2019SR0390310, \href{https://register.ccopyright.com.cn/query.html}{Beijing, China.}
%	\item \fullcite{delebecque:hal-02090402}
\end{etaremune}

% Can instead manually enter publications as shown:
% \section{Publications}
% \orderedouterlist{
% \entry{S. Petridis, J. Shen, \textbf{D. Cetin} and M. Pantic, "Visual-Only Recognition of Normal, Whispered And Silent Speech", \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), April 2018}}
% }
